Estimating duration in the presence of misclassification

### 2024-03-08 introduction.tex

Many studies involving mechanistic models were conducted during the pandemic, with at least 100 articles published in the first six months of 2020 alone~\autocite{shankarSystematic}.
In the UK, the Scientific Pandemic Influenza Group on Modelling, Operational sub-group (SPI-M-O) was a sub-committee of the Scientific Advisory Group for Emergencies (SAGE), using this type of models to generate evidence for policy development~\autocite{medleySPIM,govSPIMO}.
For example, each of the stages of lifting the lockdown in 2021 was supported by  modelling studies informing the government's decision~\autocite{sageEvidence}.

>>>>

Many studies involving mechanistic models were conducted during the pandemic, with at least 100 articles published in the first six months of 2020 alone~\autocite{shankarSystematic}.
In the UK, SPI-M-O (Scientific Pandemic Influenza Group on Modelling, Operational sub-group) was a sub-committee of SAGE (the Scientific Advisory Group for Emergencies), using this type of models to generate evidence for policy development~\autocite{medleySPIM,govSPIMO}.
For example, each of the stages of lifting the lockdown in 2021 was supported by  modelling studies informing the government's decision~\autocite{sageEvidence}.
